HGIS Carbonate Results

### 2021-06-23 doc/data_meeting_2021-06-22/data_meeting_2021-06-22.Rmd
Update to allow blank correction with only one blank.

```{r}
# Read data. Don't use first carbonate test or smaller samples.
results_df <- read_csv(here("data_analysed/carb_all_results.csv"))
cons_df <- results_df %>% 
  filter(!is.na(sig_fm_corr),
         wheel != "USAMS061121") %>% 
  mutate(he12C = he12C * 1E6) %>% 
  compare_consensus()
```

>>>>

```{r}
# Read data. Don't use first carbonate test or smaller samples.
results_df <- read_csv(here("data_analysed/carb_all_results.csv"))
cons_df <- results_df %>% 
  filter(!(wheel %in% c("USAMS020521", "USAMS061121", "USAMS061821"))) %>% 
  mutate(he12C = he12C * 1E6) %>% 
  compare_consensus()
```
